### 2022-03-01 manuscript.tex
more additions to manuscript and references

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

@@

\begin{table}[h!]
\centering
 \begin{tabular}{|c c c|} 
 \hline
 Family & param1 & param2 \\ [0.5ex] 
 \hline
 lnorm & 1 & 0.4 \\ 
 \hline
 \end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\label{tab:dbins}
 \begin{tabular}{|c|c|} 
 \hline
    bin & prob \\ \hline
    ... & ... \\
    {[1.4,\;1.6)} & 0.04414 \\
    {[1.6,\;1.8)} & 0.05896 \\
    {[1.8,\;2.0)} & 0.07032 \\
    {[2.0,\;2.2)} & 0.07172 \\
    {[2.2,\;2.4)} & 0.07955 \\
    ... & ... \\
 \hline
 \end{tabular}
\end{table}
Submitted as a forecast prediction, the distribution in table \ref{tab:dbins} 
includes 82 pieces of data. For parts 
of the CDC influenza competition some forecasts included upt to 262. This is 
much more manageable than possible thousands of samples from a samle 
distribution but is 
still much larger than the 3 or 5 data pieces required to report a lognormal
or truncated lognormal distribution.

@@

A mixture distribution may be much more flexible than a simple parametric in 
terms of distributional shape. But as it is essentially parametric, forecasters
mays still be limited in how they construct their models. But it may be possible
to fit a mixture distribution to probability models with the other 
representations discussed. Further discussion on methods for fitting mixture 
distributions to different types of model representations is included in this 
paper.

@@

Tools for creating a discrete mixture distribution as well as constructing an 
ensemble model from several mixture distributions are

\subsection{Tools for a discrete mixture}

\section*{MakeDist}
The MakeDist function is applied function over an R dataframe and returns an 
object of class "UnivarMixingDistribution"

\subsection*{Usage}
MakeDist(df)

>>>>

@@

\begin{table}[h!]
\label{tab:pstor}
\centering
 \begin{tabular}{|c c c|} 
 \hline
 Family & param1 & param2 \\ [0.5ex] 
 \hline
 lnorm & 1 & 0.4 \\ 
 \hline
 \end{tabular}
\end{table}

@@

\begin{table}[h!]
\label{tab:dstor}
\centering
 \begin{tabular}{|c|c|} 
 \hline
    bin & prob \\ \hline
    ... & ... \\
    {[1.4,\;1.6)} & 0.04414 \\
    {[1.6,\;1.8)} & 0.05896 \\
    {[1.8,\;2.0)} & 0.07032 \\
    {[2.0,\;2.2)} & 0.07172 \\
    {[2.2,\;2.4)} & 0.07955 \\
    ... & ... \\
 \hline
 \end{tabular}
\end{table}
Submitted as a forecast prediction, the distribution in table \ref{tab:dstor} 
includes 82 pieces of data. For parts 
of the CDC influenza competition some forecasts included upt to 262. This is 
much more manageable than possible thousands of samples from a samle 
distribution but is 
still much larger than the 3 or 5 data pieces required to report a lognormal
or truncated lognormal distribution.

@@

A mixture distribution may be much more flexible than a simple parametric in 
terms of distributional shape. But as it is essentially parametric, forecasters
mays still be limited in how they construct their models. But it may be possible
to fit a mixture distribution to probability models with the other 
representations discussed. According to McLachlan and Peel, a finite mixture of 
normal densities with common variance can be used to approximate abitrarily well
any continuous distribution \cite{peel2000finite} (see also 
\cite{nguyen2019approximations}). Thus, for any unconventional probability
distribution -such as MCMC posterior samples- it may be reasonable to 
approximate the distribution by a mixture of normals.
Further discussion on methods for fitting mixture 
distributions to different types of model representations is included in this 
paper.

@@

The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
have their own established systems for receiving, 
evaluating and constructing ensemble forecasts. A transition from using binned 
distributions or quantile forecasts to using mixture distributions would require
a few adjustments to those systems. In this section we outline how some of these
adjustments may be implemented as well as present some tools which may be used
to evaluate forecasts and construct ensemble forecasts from multiple models.

\subsection{Submission format}
For a collaborative forecast project to run smoothly, model submissions from all 
modelers should all follow the same format. For both the CDC flu forecasting and
the COVID-19 Forecast Hub, teams are provided a csv spreadsheet with columns 
similar to those in tables \ref{tab:dstor} and \ref{tab:qstor}. Additionally
columns for Location, Target, Type and Unit are included which serve as
indicators of the specific prediction. The values for all variables except 
Value come from a specified list from the forecast center. Value is the 
probability assigned to a bin when the Type is Bin.

\begin{table}[h!]
\label{tab:dstan}
\centering
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
    Location & Target & Type & Unit & Bin & Value  \\ \hline
    US National & Season Onset & Point & week & NA & . \\
    US National & Season Onset & Bin & week & 0.0 & . \\
    US National & Season Onset & Bin & week & 0.1 & . \\
    ... & ... & ... & ... & ... & ... \\
 \hline
 \end{tabular}
\end{table}

For the quantile forecasts of the Forecast Hub, the possible values for Type 
are Point and Quantile, and rather than using a Bin variable Quantile is used
with values specified by the Hub. Then Value rather than a probability is the
forecasted value for the specified quantile. Per prediction there may be a 
couple dozen rows, up to 24 in the Forecast Hub, or over 100 rows as in some
flu forecasts.

An adjustment may be made to the format of table \ref{tab:dstan} where each row
represents a compnonent in a mixture distribution.
The variables Bin/Quantile and Value are removed and replaced with Family,
Param1, Param2, Param3 and Weight where Family is the distribution family,
Params are the parameters for the component distribution and Weight is the 
weight $w_i$ for that component.

\begin{table}[h!]
\label{tab:mstan}
\centering
 \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 \hline
    Location & Target & Type & Unit & Family & Param1 & Param2 & Param3 & Weight
    \\ \hline
    US National & Season Onset & Dist & week & norm & mean & sd & NA & .  \\
    US National & Season Onset & Dist & week & lnorm & meanlog & sdlog & NA & . \\
    ... & ... & ... & ... & ... & ... & ... & ... & .\\
 \hline
 \end{tabular}
\end{table}

A forecast center may want to limit the number of components allowed per 
prediction. For a reference, a mixture distribution prediction with 16 
components would require $16 \times 9 = 144$ cells submitted. This is the same 
number of cells
submitted for a Forecast Hub forecast with 23 quantiles and a point prediction.

\subsection{Mixture construction and scoring tools}

From a submitted forecast, a prediction may be found by Location, Target and 
Unit (or whatever other indication variables are used) and evaluated. We found
the \texttt{distr} \cite{camphausen2007distr}
useful for constructing a mixture distribution given
information like that from table \ref{tab:mstan}.

The function 
\texttt{UnivarMixingDistribution} takes as arguments a list of distributions
and a vector of weights for each distribution and a object pf a class called 
\texttt{AbscontDistribution} is returned. Functions for density, distribution
and quantile functions as well as for random sampling may then be used on the
mixture distribution object for evaluation. Using those functions and the 
created object, LogS and CRPS are easily calculable.

We wrote a function \texttt{MakeDist} which takes on a data frame with variables
Family, Param1, Param2, Param3 and Weight and returns a mixture distribution 
of component distributions specified in the rows.

\subsection{Ensemble construction}

To construct an ensemble distribution from multiple mixture distributions, the 
\texttt{UnivarMixingDistribution} is again a useful tool. Two or more 
\texttt{AbscontDistribution} objects may be
